Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-10-31 src/tex/ms.tex
Update ms.tex

In Section \ref{sec:simulations} we discuss our assumptions used in 
simulating DWD populations and detail the process to produce present-day 
synthetic Milky-Way-like galaxies. In Section \ref{sec:LISA_obs} we review 
the derivation of LISA detectability for circular DWD populations at mHz 
frequencies. In Section \ref{sec:results} we detail results showing how a 
metallicity-dependent binary fraction affects the formation and evolution 
of DWD populations assuming four sets of of binary evolution assumptions. 
In Section \ref{sec:LISA_met} we detail the metallicity dependence of the 
LISA DWD foreground and resolved population. Finally, we consider how a 
metallicity-dependent close binary fraction impacts the height of the 
Galactic DWD foreground in LISA for different binary evolution assumptions 
in Section \ref{sec:model_compare} and conclude in Section 
\ref{sec:conclusions}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/met_dep_porb.pdf}
    \caption{The distribution of the companion frequency f$_{\rm{logP}}$ 
for solar-type stars is dependent on both ZAMS orbital period and 
metallicity. Each curve is coloured by metallicity, with the darkest curve 
corresponding to the lowest-metallicity bin in our simulations at [Fe/H] 
$=-2.3$ and the lightest curve corresponding to our highest-metallicity 
bin at [Fe/H] $=0.18$. Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the 
companion frequency distribution is the same for all metallicity bins as 
no identified metallicity dependence at those periods exists in current 
literature.}
    \label{fig:met_dep_porb}
    \script{met_dep_porb.py}
\end{figure}

@@

\[f_{\rm{b}}= \begin{cases} 
      - 0.0648 \cdot [\rm{Fe/H}] + 0.3356, & [\rm{Fe/H}]\leq -1.0 
\numberthis \\
      -0.1977 \cdot [\rm{Fe/H}] + 0.2025, & [\rm{Fe/H}]> -1.0  , 
   \end{cases}
\]

@@

We discard any DWDs for which the sum of their ZAMS birth time, given by 
the star particle formation time, and DWD formation time is larger than 
the age of the star particle since the system will not have evolved long 
enough to become a DWD at present. We further discard any DWDs for which 
the lower mass WD overflows it's Roche lobe before present day, because 
the outcomes of these interactions are highly uncertain and their 
treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, 
Kremer2017}. This choice does not significantly affect our results since 
stably accreting WD binaries are unlikely to contribute appreciably to the 
Galactic DWD foreground due to their small mass ratios at frequencies 
below 1 mHz \citep{Breivik2018}. The separation at which the lower mass WD 
overflows its Roche Lobe is defined as

\begin{equation}
    a_{\text{RLO,}\ell} = R_{\ell} \frac{0.6 q_{\ell}^{2/3} + 
\ln{(1+q_{\ell}^{1/3})}}{0.49 q_{\ell}^{2/3}}
\end{equation}
where $R_{\ell}$ is the radius of the lower mass WD and $q_{\ell} = 
M_{\ell}/M_{h}$ is the ratio of the lower- to higher-mass WD components. 
\citep{Eggleton1983}. 
We define the radius of a WD following \citet{Tout1997, Hurley2000} as
\begin{equation}
    R_{\rm{WD}} = \max\Bigg(R_\text{NS}, 
0.0115\sqrt{\left(\frac{M_\text{Ch}}{M}\right)^{2/3}-\left(\frac{M}{M_\text{Ch}}\right)^{2/3}} 
\Bigg) 
\end{equation}
\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}~R_\odot$ is the radius of 
a neutron star, $M_{\text{Ch}}=1.44 ~M_\odot$ is the Chandrasekhar limit 
for the mass of a stable WD, and $M$ is the mass of the WD in solar 
masses.

@@

To lowest order in the post-Newtonian expansion, the frequency evolution 
of circular orbits for quadrupole GW emission is defined as
\begin{equation}
    \Dot{f}_n = \frac{48n}{5\pi} \frac{(G\mathcal{M}_c)^{5/3}}{c^5} (2\pi 
f_\text{orb})^{11/3}.
\end{equation}
We classify DWDs as evolving, or ``chirping", when $\Dot{f}_n \geq 
1/t_\text{obs}^2$. For evolving sources, the SNR is

@@

ONe WDs are rare and typically form from massive progenitor stars which 
evolve through the asymptotic giant branch phase, thus resulting in a 
higher mass WD. All ONe WDs in our \cosmic\ populations, e.g., have 
progenitor ZAMS masses above $4\,M_\odot$, and the resulting ONe WDs have 
a relatively flat distribution of masses from $1.05\,M_\odot$ up to the 
Chandrasekkhar limit of $1.4\,M_\odot$. Because an ONe WD can have a 
companion of any other WD type in our study, there is a spread in their 
distributions for separation, secondary mass, final orbital period, and 
formation time. In general, however, these systems result from wider 
separations to allow for the evolution of the ONe component without 
merging. For example, all initial separations in our \cosmic \ populations 
have separations $\gtrsim 1.5\,R_\odot$. ONe + X DWDs can form on short 
timescales, as low as $30\,\rm{Myr}$, for the majority of high-metallicity 
systems.

@@

\textbf{There are two common ways that the formation of DWDs from stellar 
progenitors is inhibited. The first is through stellar mergers, where the 
binary merges before both components become WDs. The second is due to 
evolutionary outcomes like forming a different DWD type, or not forming a 
DWD by the present day. For all DWD types except ONe + X, which has other 
dominating affects hindering formation efficiency like 
metallicity-dependent stellar winds, we find that different regimes of 
ZAMS orbital period leads to different specific evolutionary channels.}

\textbf{In our \cosmic\ models, lower-metallicity stars evolve faster than 
high-metallicity stars and have larger radii near the end of the MS. This 
changes the timescales of RLO: low-metallicity stars tend to fill their 
Roche lobes while still on the MS, meaning mass transfer can remain stable 
which serves to widen the binary. In contrast, high-metallicity systems 
initiate mass transfer after the donor has left the main sequence, so the 
binary is more likely to enter a CE phase. Moreover, high-metallicity 
progenitors tend to have deeper convective envelopes such that a larger 
fraction of their mass is contained in the envelope relative to 
lower-metallicity counterparts of the same mass \citep{Amard2019, 
Amard2020}. When these systems enter a CE phase, it thus requires more 
orbital energy to eject the CE than for a low-metallicity star at the same 
point in its evolution, causing a large amount of orbital shrinking. These 
effects often leads to a stellar merger at higher metallicities for a 
system that would have survived the CE phase at a lower metallicity, thus 
causing a decrease in formation efficiency with metallicity.}

The skews introduced by the metallicity-dependent ZAMS orbital period 
distribution and binary fraction of FZ also contribute to the formation 
efficiency trends. The log-normal metallicity-dependent $P_{\rm{orb}}$ 
distribution increasingly skews towards orbital periods below 10$^4$ days 
for decreasing metallicity. This amplifies the effects of 
metallicity-dependent stellar evolution discussed above. For example, the 
skew induces more mergers at high metallicities where the deeper 
convective envelope leads to increased orbital shrinkage. However, it is 
also of note that the log-uniform orbital period distribution of F50 
produces a higher number of the shortest-orbital period systems (below 
$\sim100$ days) than FZ, since the tails of the FZ distribution fall 
quickly below this threshold. These systems also have a propensity for 
merging before the formation of a DWD.

@@

Figure \ref{fig:CEsep} shows the average separation at the first instance 
of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in 
systems orbiting in the LISA frequency band at present day, as a function 
of metallicity for each DWD type. The solid lines denote the average 
value, and the $1\sigma$ variance is shown in the surrounding shading. We 
show this for our fiducial variation and each of our binary parameter 
variations. For our fiducial, $\alpha25$ and $\alpha5$ parameter 
variations, the average CE separation increases in general across 
metallicity. Higher-metallicity binaries will interact earlier in the 
binary's lifetime than a lower-metallicity binary of equal separation due 
to their relatively larger maximum radii. Since higher-metallicity 
binaries are also more likely to merge during CE interactions because of 
their relatively more massive donor envelopes, the DWDs which survive and 
eventually orbit in the LISA band originate from systems with higher 
interaction separations which allow their orbits to shrink significantly 
during CE phases without merging. This regulation plays a key role in 
smearing out any observable effects of a metallicity-dependent binary 
fraction in the population of DWDs observable by LISA.

@@

\begin{figure*}

\includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
    \caption{The chirp mass vs distance for each DWD type is shown for our 
fiducial parameter variation. Only systems with observable evolution in 
their GW frequency, i.e those which are chirping, and with SNR $>7$, are 
shown, since these are systems for which distance can be separated from 
chirp mass within their strain amplitude. Each panel shows one DWD type, 
summed over all metallicities. Model FZ is indicated with solid light blue 
contours, and model F50 is indicated with dark blue dashed contours 
respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 
50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite 
intrinsic changes to population properties induced by a 
metallicity-dependent binary fraction, and a reduction in the height of 
the DWD Galactic foreground the distributions are very similar.}
    \label{fig:Mc_vs_dist}
    \script{Mc_vs_dist.py}
\end{figure*}

@@

Similar to previous studies, we find that LISA will be able to resolve 
several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude 
spectral density vs GW frequency of the resolved systems with SNR $> 7$ 
for each DWD type, where the top and bottom rows show results for models 
FZ and F50 respectively for the fiducial parameter variation. For 
comparison, we also show the LISA sensitivity curve, including the 
modeled confusion foreground from each population in black, and the the 
entire population for each model in grey. Plots for our three parameter 
variations can be found in Appendix \ref{appendix:ASD_vars}. Apart from 
each DWD type having a different abundance of resolved systems, the 
population-wide characteristics remain unchanged between the two binary 
fraction models. The populations containing at least one He WD occupy the 
lower-ASD, higher-GW frequency region of parameter space compared to the 
total population, with CO + He DWDs having larger ASDs than the He + He 
DWD population. Conversely, DWD types without a He WD component tend to 
occupy the higher-ASD, lower-GW frequency region of parameter space. This 
difference is largely due to the formation scenario of DWDs containing a 
He WD, which form from the ejection of a common envelope created by the He 
WD progenitor. These lower mass progenitors overflow their Roche lobes at 
closer separations relative to the higher mass progenitors (e.g. 
Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the 
distance to any one DWD strongly influences its ASD, DWD populations 
without a He WD component have, on average, higher ASDs due to their more 
massive WD components.

We note that the height of the confusion foreground and the number of DWDs 
radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor 
of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, 
the number of resolved sources is not reduced to an equal degree. This is 
because in the absence of less competing GW signals from DWDs in the LISA 
frequency band, more DWDs can be individually resolved. For the fiducial 
and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ 
are reduced by 4.5\% and increased by 3\% respectively. However, for 
$\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the 
number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% 
reduction even though the overall LISA population of both variations is 
halved. A large portion of the maintenance of the number of DWDs in 
parameter variation $q3$ is contributed to by He + He binaries with higher 
GW frequencies and lower ASDs which can now survive CE interactions due to 
an initial phase of mass transfer (see discussion of this formation 
channel in Section \ref{sec:CEsep}).

@@

In each parameter variation, changing the binary evolution assumptions 
dramatically changes the formation and evolution of the DWD populations. 
These changes lead to large shifts in the overall number of close DWDs in 
our synthetic present-day Milky-Way-like galaxies. We find that the total 
number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both 
variations $q3$ and $\alpha5$. This is because there are fewer stellar 
mergers which occur before the formation of a DWD, thus allowing more 
systems to evolve due to GW emission and orbit in the LISA frequency band 
at present. Conversely, for variation $\alpha25$, we find that the number 
of DWDs orbiting with frequencies in the LISA band is drastically reduced. 
This is because of the highly inefficient use of orbital energy to eject 
the common envelope, thus producing more stellar mergers, or closer 
binaries which are more prone to future mergers.

Interestingly, when we compare the populations of each binary fraction 
model for our variations, we find that the number of close DWDs remains 
approximately unchanged for our fiducial set of assumptions and $\alpha25$ 
variation, but is reduced by 50\% for variations $\alpha5$ and $q3$. This 
is illustrated in Figure \ref{fig:model_comp}. The top panel shows the 
confusion foreground fits for each binary evolution variation (different 
colored lines) and for each binary fraction model where the solid lines 
show FZ models and dotted lines show F50 models. The bottom panel shows 
the ratio of the number of DWDs orbiting in the LISA frequency band for 
the FZ models vs the F50 models for each variation. The number of DWDs in 
the LISA band spans over two orders of magnitude, and the ratio of FZ to 
F50, as well as the spectral shape of the confusion fit, is either 
relatively unchanged or reduced by a factor of approximately two. This 
suggests that assuming a metallicity-dependent binary fraction may change 
the size of the Galactic close DWD population by a factor of $\sim$ two 
and the strength of the Galactic DWD GW foreground for LISA depending on 
the chosen binary evolution model.

\section{Conclusions}\label{sec:conclusions}
In this study, we have investigated the effects of assuming a 
metallicity-dependent binary fraction on the formation and evolution of 
the Galactic population of DWDs with a special focus on the implications 
for LISA. Based on our synthetic Milky-Way-like galaxy catalogs of DWDs, 
we find that applying a metallicity-dependent binary fraction changes the 
formation efficiency and evolutionary history of DWD populations. However, 
when considering the close DWD populations observable by LISA, we find 
that the only distinguishing features between models which assume a 
metallicity-dependent binary fraction (model FZ) and models which assume a 
flat $50\%$ binary fraction (model F50) are the population sizes and the 
strength of the Galactic DWD GW foreground. Models which assume a 
metallicity-dependent binary fraction produce Galactic DWD populations 
that were unchanged relative to the standard model assumptions. However, 
our results are highly dependent on the chosen binary evolution model. We 
extended our study to include three binary evolution parameter variations 
to investigate the sensitivity of the DWD population changes in 
assumptions for mass transfer stability and common envelope ejection 
efficiencies. While our binary evolution parameter variations change the 
size of the LISA-observable populations dramatically, the size of the 
close Galactic DWD population and the height of the confusion foreground 
for models which assume a metallicity-dependent binary fraction appears to 
either remain unchanged \emph{or} be reduced by 50\%. This reduction 
extends to the height of the confusion foreground in the LISA data stream. 
These two results highlight the interplay between the dominating factors 
which shape the LISA DWD population: the metallicity-dependent star 
formation history of the \textbf{m12i} galaxy, the metallicity-dependent 
close binary fraction which alters the ZAMS orbital period distribution, 
and the impact of binary evolution assumptions on DWD formation. This 
comparison emphasizes the sensitivity of the Galactic population of 
LISA-detectable DWDs to the intricacies of binary evolution. Binary 
evolution assumptions like CE efficiency are undergoing continuous study 
in current literature and an exact value has yet to be identified. By 
exploring a range of possibilities in this work, we capture the variation 
in predictions of the LISA DWD population that may be observed.

@@

\appendix
\section{\textbf{Formation efficiency trends}}\label{appendix:form_eff}
\textbf{As discussed in Section \ref{sec:formeff}, the formation 
efficiency of DWDs exhibitis a metallicity dependence. This is both due to 
the impact of metallicity on stellar evolution, and on the ZAMS orbital 
period distribution of model F50 vs. FZ. Each DWD type and binary 
evolution parameter variation exhibits unique trends in efficiency and in 
their evolutionary channel. In the following subsections we go through 
each DWD type in detail, first for our fiducial simulations and then for 
our variations.}

@@

For CO + He DWD progenitor systems with intermediate orbital periods 
($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which 
impact formation efficiency are complex. The dominant way CO + He DWDs 
\textbf{fail to form} is stellar mergers that occur during the second CE 
phase. \textbf{Low-metallicity systems survive this second CE phase 
whereas high-metallicity systems do not.} \textbf{Similar to the 
short-period systems, there is increased orbital shrinkage for 
high-metallicity progenitor binaries due to the deeper convective envelope 
of the CE evolution donor. This creates shorter post-CE orbital periods 
which leads to mergers during the CE second phase.}

@@

\subsubsection{\textbf{ONe + X}}\label{formeff_ONe}
The strongest effect which hinders formations of higher-metallicity ONe + 
X DWDs is the strength of metallicity-dependent stellar winds assumed in 
our model \citep{Vink2001}. The strength of line-driven winds varies more 
strongly for the more massive ($\geq5\,M_\odot$) progenitors of ONe WDs 
relative to the other lower mass WD progenitors. At higher metallicities, 
ONe WD progenitors can lose enough mass through winds such that they don't 
ignite their CO cores and thus leave behind a CO WD. Conversely, the 
lower-metallicity progenitors retain enough mass to cause carbon ignition 
and leave behind an ONe WD.

@@

Beyond the effects described above, the efficiency drop across metallicity 
is similar to the fiducial parameter variation in that it depends on the 
metallicity-dependent ZAMS orbital period distribution emphasizing 
short-period systems at low metallicities, and on the change of formation 
channel for different period ranges across metallicity. We find the 
variation $q3$ yields the highest formation efficiency. Only the 
shortest-period binaries do not form a DWD\textbf{, which are lost} 
through mergers at higher metallicities. At low metallicities, even 
binaries with ZAMS orbital periods $P_{\rm{orb}}\lesssim 100$ days form He 
+ He DWDs, with binaries in model FZ reaching ZAMS orbital periods less 
than a day in length. This leads to a higher formation efficiency from F50 
over FZ for parameter variation $q3$ because of the higher number of 
shortest-period ZAMS binaries in the log-uniform distribution of F50.

>>>>

In Section \ref{sec:simulations} we discuss our assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies. In Section \ref{sec:LISA_obs} we review the derivation of LISA detectability for circular DWD populations at mHz frequencies. In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming four sets of of binary evolution assumptions. In Section \ref{sec:LISA_met} we detail the metallicity dependence of the LISA DWD foreground and resolved population. Finally, we consider how a metallicity-dependent binary fraction impacts the height of the Galactic DWD foreground in LISA for different binary evolution assumptions in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/met_dep_porb.pdf}
    \caption{The distribution of the companion frequency f$_{\rm{logP}}$ for solar-type stars is dependent on both ZAMS orbital period and metallicity. Each curve is coloured by metallicity, with the darkest curve corresponding to the lowest-metallicity bin in our simulations at [Fe/H] $=-2.3$ and the lightest curve corresponding to our highest-metallicity bin at [Fe/H] $=0.18$. Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no identified metallicity dependence at those periods exists in current literature.}
    \label{fig:met_dep_porb}
    \script{met_dep_porb.py}
\end{figure}

@@

\[f_{\rm{b}}= \begin{cases} 
      - 0.0648 \, \rm{ [Fe/H]} + 0.3356, & [\rm{Fe/H}]\leq -1.0 \numberthis \\
     -0.1977 \, \rm{ [Fe/H]} + 0.2025, & [\rm{Fe/H}]> -1.0  , 
   \end{cases}
\]

@@

We discard any DWDs for which the sum of their ZAMS birth time, given by the star particle formation time, and DWD formation time is larger than the age of the star particle since the system will not have evolved long enough to become a DWD at present. We further discard any DWDs for which the lower-mass WD overflows it's Roche lobe before present day, because the outcomes of these interactions are highly uncertain and their treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, Kremer2017}. This choice does not significantly affect our results since stably accreting WD binaries are unlikely to contribute appreciably to the Galactic DWD foreground due to their small mass ratios at frequencies below 1 mHz \citep{Breivik2018}. The separation at which the lower-mass WD overflows its Roche Lobe is defined as

\begin{equation}
    a_{\text{RLO,}\ell} = R_{\ell} \frac{0.6 q_{\ell}^{2/3} + \ln{(1+q_{\ell}^{1/3})}}{0.49 q_{\ell}^{2/3}}
\end{equation}
where $R_{\ell}$ is the radius of the lower-mass WD and $q_{\ell} = M_{\ell}/M_{h}$ is the ratio of the lower- to higher-mass WD components \citep{Eggleton1983}. 
We define the radius of a WD following \citet{Tout1997, Hurley2000} as
\begin{equation}
    R_{\rm{WD}} = \max\Bigg(R_\text{NS}, 0.0115\sqrt{\left(\frac{M_\text{Ch}}{M}\right)^{2/3}-\left(\frac{M}{M_\text{Ch}}\right)^{2/3}} \Bigg) 
\end{equation}
\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}~R_\odot$ is the radius of a neutron star, $M_{\text{Ch}}=1.44 ~M_\odot$ is the Chandrasekhar limit for the mass of a stable WD, and $M$ is the mass of the WD in solar masses.

@@

To lowest order in the post-Newtonian expansion, the frequency evolution of circular orbits for quadrupole GW emission is defined as
\begin{equation}
    \Dot{f}_n = \frac{48n}{5\pi} \frac{(G\mathcal{M}_c)^{5/3}}{c^5} (2\pi f_\text{orb})^{11/3}.
\end{equation}
We classify DWDs as evolving, or ``chirping", when $\Dot{f}_n \geq 1/T_\text{obs}^2$. For evolving sources, the SNR is

@@

ONe WDs are rare and typically form from massive progenitor stars which evolve through the asymptotic giant branch phase, thus resulting in a higher-mass WD. All ONe WDs in our \cosmic\ populations, e.g., have progenitor ZAMS masses above $4\,M_\odot$, and the resulting ONe WDs have a relatively flat distribution of masses from $1.05\,M_\odot$ up to the Chandrasekkhar limit of $1.4\,M_\odot$. Because an ONe WD can have a companion of any other WD type in our study, there is a spread in their distributions for separation, secondary mass, final orbital period, and formation time. In general, however, these systems result from wider separations to allow for the evolution of the ONe component without merging. For example, all initial separations in our \cosmic \ populations have separations $\gtrsim 1.5\,R_\odot$. ONe + X DWDs can form on short timescales, as low as $30\,\rm{Myr}$, for the majority of high-metallicity systems.

@@

\textbf{There are two common ways that the formation of DWDs from stellar progenitors is inhibited. The first is through stellar mergers, where the binary merges before both components become WDs. The second is due to evolutionary outcomes like forming a different DWD type, or not forming a DWD by the present day. For all DWD types except ONe + X, which has other dominating \textbf{effects} hindering formation efficiency like metallicity-dependent stellar winds, we find that different regimes of ZAMS orbital period leads to different specific evolutionary channels.}

\textbf{In our \cosmic\ models, lower-metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS. This changes the timescales of RLO: low-metallicity stars tend to fill their Roche lobes while still on the MS, meaning mass transfer can remain stable which serves to widen the binary. In contrast, high-metallicity systems initiate mass transfer after the donor has left the main sequence, so the binary is more likely to enter a CE phase. Moreover, high-metallicity progenitors tend to have deeper convective envelopes such that a larger fraction of their mass is contained in the envelope relative to lower-metallicity counterparts of the same mass \citep{Amard2019, Amard2020}. When these systems enter a CE phase, it thus requires more orbital energy to eject the CE than for a low-metallicity star at the same point in its evolution, causing a large amount of orbital shrinking. These effects often leads{\sout{s}} to a stellar merger at higher metallicities for a system that would have survived the CE phase at a lower metallicity, thus causing a decrease in formation efficiency with metallicity.}

The skews introduced by the metallicity-dependent ZAMS orbital period distribution and binary fraction of FZ also contribute to the formation efficiency trends. The log-normal metallicity-dependent $P_{\rm{orb}}$ distribution increasingly skews towards orbital periods below 10$^4$ days for decreasing metallicity. This amplifies the effects of metallicity-dependent stellar evolution discussed above. For example, the skew induces more mergers at high metallicities where the deeper convective envelope leads to increased orbital shrinkage. However, it is also of note that the log-uniform orbital period distribution of F50 produces a higher number of the shortest-orbital period systems (below $\sim100$ days) than FZ, since the tail of the FZ distribution falls quickly below this threshold. These systems also have a propensity for merging before the formation of a DWD.

@@

Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $\overline{\mathrm{a}}_{\rm{CE}}$, of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type. The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading. We show this for our fiducial variation and each of our binary parameter variations. For our fiducial, $\alpha25$ and $\alpha5$ parameter variations, the average CE separation increases in general across metallicity. Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii. Since higher-metallicity binaries are also more likely to merge during CE interactions because of their relatively more massive donor envelopes, the DWDs which survive and eventually orbit in the LISA band originate from systems with higher interaction separations which allow their orbits to shrink significantly during CE phases without merging. This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
    \caption{The chirp mass vs distance for each DWD type is shown for our fiducial parameter variation. Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude. Each panel shows one DWD type, summed over all metallicities. Model FZ is indicated with solid light blue contours, and model F50 is indicated with dark blue dashed contours respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction, and a reduction in the height of the DWD Galactic foreground the distributions are very similar.}
    \label{fig:Mc_vs_dist}
    \script{Mc_vs_dist.py}
\end{figure*}

@@

Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation. For comparison, we also show the LISA sensitivity curve, including the 
modeled confusion foreground from each population in black, and the the entire population for each model in grey. Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}. Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models. The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population. Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space. This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor. These lower-mass progenitors overflow their Roche lobes at closer separations relative to the higher-mass progenitors (e.g. Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.

We \textbf{highlight} that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, the number of resolved sources is not reduced to an equal degree. This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved. For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by 4.5\% and increased by 3\% respectively. However, for $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% reduction even though the overall LISA population of both variations is halved. A large portion of the maintenance of the number of DWDs in parameter variation $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).

@@

In each parameter variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations. These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky-Way-like galaxies. We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$ \textbf{with respect to the fiducial case}. This is because there are fewer stellar mergers which occur before the formation of a DWD, thus allowing more systems to evolve due to GW emission and orbit in the LISA frequency band at present. Conversely, for variation $\alpha25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced. This is because of the highly inefficient use of orbital energy to eject the common envelope, \textbf{which produces} more stellar mergers, or closer binaries which are more prone to future mergers.

Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$. This is illustrated in Figure \ref{fig:model_comp}. The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation. The number of DWDs in the LISA band spans over two orders of magnitude, \textbf{but} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, is either relatively unchanged or reduced by a factor of approximately two. This suggests that assuming a metallicity-dependent binary fraction may change the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA depending on the chosen binary evolution model.

\section{Conclusions}\label{sec:conclusions}
In this study, we have investigated the effects of assuming a metallicity-dependent binary fraction on the formation and evolution of the Galactic population of DWDs with a special focus on the implications for LISA. Based on our synthetic Milky Way-like galaxy catalogs of DWDs, we find that applying a metallicity-dependent binary fraction changes the formation efficiency and evolutionary history of DWD populations. However, when considering the close DWD populations observable by LISA, we find that the only distinguishing features between models which assume a metallicity-dependent binary fraction (model FZ) and models which assume a flat $50\%$ binary fraction (model F50) are the population sizes and the strength of the Galactic DWD GW foreground. Models which assume a metallicity-dependent binary fraction produce Galactic DWD populations that were unchanged relative to the standard model assumptions. However, our results are highly dependent on the chosen binary evolution model. We extended our study to include three binary evolution parameter variations to investigate the sensitivity of the DWD population changes in assumptions for mass transfer stability and common envelope ejection efficiencies. While our binary evolution parameter variations change the size of the LISA-observable populations dramatically, the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction appears to either remain unchanged \emph{or} be reduced by 50\%. These two results highlight the interplay between the dominating factors which shape the LISA DWD population: the metallicity-dependent star formation history of the \textbf{m12i} galaxy, the metallicity-dependent close binary fraction which alters the ZAMS orbital period distribution, and the impact of binary evolution assumptions on DWD formation. This comparison emphasizes the sensitivity of the Galactic population of LISA-detectable DWDs to the intricacies of binary evolution. Binary evolution assumptions like CE efficiency are undergoing continuous study in current literature and an exact value has yet to be identified. By exploring a range of possibilities in this work, we capture the variation in predictions of the LISA DWD population that may be observed.

@@

\appendix
\section{\textbf{Formation efficiency trends}}\label{appendix:form_eff}
\textbf{As discussed in Section \ref{sec:formeff}, the formation efficiency of DWDs exhibits a metallicity dependence. This is due to the impact of metallicity on \textbf{both} stellar evolution, and the ZAMS orbital period distribution of model F50 vs. FZ. Each DWD type and binary evolution parameter variation exhibits unique trends in efficiency and in their evolutionary channel. In the following subsections we go through each DWD type in detail, first for our fiducial simulations and then for our variations.}

@@

For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex. The dominant way CO + He DWDs \textbf{fail to form} is stellar mergers that occur during the second CE phase. \textbf{Low-metallicity systems survive this second CE phase whereas high-metallicity systems do not.} \textbf{Similar to the short-period systems, there is increased orbital shrinkage for high-metallicity progenitor binaries due to the deeper convective envelope of the CE evolution donor. This creates shorter post-CE orbital periods which leads to mergers during the second \textbf{CE} phase.}

@@

\subsubsection{\textbf{ONe + X}}\label{formeff_ONe}
The strongest effect which hinders formations of higher-metallicity ONe + X DWDs is the strength of metallicity-dependent stellar winds assumed in our model \citep{Vink2001}. The strength of line-driven winds varies more strongly for the more massive ($\geq5\,M_\odot$) progenitors of ONe WDs relative to the other lower-mass WD progenitors. At higher metallicities, ONe WD progenitors can lose enough mass through winds such that they don't ignite their CO cores and thus leave behind a CO WD. Conversely, the lower-metallicity progenitors retain enough mass to cause carbon ignition and leave behind an ONe WD.

@@

Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and on the change of formation channel for different period ranges across metallicity. We find \textbf{that} variation $q3$ yields the highest formation efficiency. Only the shortest-period binaries do not form a DWD\textbf{, which are lost} through mergers at higher metallicities. At low metallicities, even binaries with ZAMS orbital periods $P_{\rm{orb}}\lesssim 100$ days form He + He DWDs, with binaries in model FZ reaching ZAMS orbital periods less than a day in length. This leads to a higher formation efficiency from F50 over FZ for parameter variation $q3$ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.
